Waving and swaying

### 2013-09-17 Paper/grass.tex
Modified author ordering
Updated dashing abstract.

\title{Waving and swaying}
\author{Ravi Singh}
\author{Shreyas Mandre}
\affiliation{Brown University, Providence RI 02912 USA}
\author{Mahesh Bandi\footnote{work performed while visiting Brown University}}
\affiliation{Okinawa Institute of Science and Technology, Okinawa, Japan}
\author{Amala Mahadevan}
\affiliation{Woods Hold Institute of Oceanography, Woods Hole MA USA}
\author{L. Mahadevan}
\affiliation{Harvard University, Cambridge MA 02138 USA}

\begin{abstract}
%We propose a coupled fluid-canopy model to study dynamics of canopy as well as flow field of fluid. The presence of 
%vegetation is incorporated as a continuous medium which is coupled to flow field via a drag term. We
%did stability analysis of mean flow having strong shear near tip of canopy via solving modified form of 
%Orr-Somerfield equation which has some extra term due to coupling of grass and flow field. Our calculation
%predicts existence of threshold velocity for synchronous waving to commence which have been experienced in different field observations

Flow through submerged aquatic vegetation generates coherent vortices on top of vegetation depending on flow strength and vegetation 
properties, generation of coherent vortices are understood to be manifestation of a hydrodynamic instability of fluid flow experiencing 
different amount of drag force in and out of vegetation. In this study we propose a mechanism based on coupled fluid-vegetation model where presence of vegetation is incorporated 
as a continuous medium coupled to flow field via a drag term. It is predicted that in case of submerged vegetation with high number density,
wave length of coherent vortices are %not governed by shear length scale $L_s = U(h)/U^{'}(h)$ near tip of vegetation 
%(where h is vegetation height, $U(z)$ is mean velocity as function of $z$ and $U'(z) =dU/dz$)
controlled by unvegetated water channel height. Mechanism also predicts existence of threshold velocity for coherent vortices to be observed.     
\end{abstract}
\maketitle

>>>>

\title{Waving and swaying}
\author{Ravi Singh}
\affiliation{Brown University, Providence RI 02912 USA}
\author{L. Mahadevan}
\affiliation{Harvard University, Cambridge MA 02138 USA}
\author{Mahesh Bandi\footnote{work performed while visiting Brown University}}
\affiliation{Okinawa Institute of Science and Technology, Okinawa, Japan}
\author{Amala Mahadevan}
\affiliation{Woods Hold Institute of Oceanography, Woods Hole MA USA}
\author{Shreyas Mandre}
\affiliation{Brown University, Providence RI 02912 USA}

\begin{abstract}
The spontaneous waving of marine grass is thought to be due to a Kelvin-Helmholtz instability resulting from an inflection point in the flow profile. We find that this inflection point is located inside the grass canopy, and the drag from the grass blades damps out the Kelvin Helmholtz instability, normally observed in a free shear layer. We also show that the wavelength of coherent vortices scales with the unvegetated water depth, and not with the shear layer thickness as predicted by a theory based on Kelvin-Helmholtz instability. Based on these results, we propose a mechanism for waving marine grass based on the shear instability of the flow above the canopy.
\end{abstract}
\maketitle
